Figures to insert in text

### 2018-02-27 Chapters/sdm-applications.tex
Chapter 02 SDM

\section{Results (iii): Noise filtering application}

@@

>>>>

\section{Results (iii): Supervised image noise filtering application}

Image noise filtering consists in removing the noise from an input, in out case an image. Our images are black \& white images and the noise is generated randomly flipping some of their pixels from black to while and vice versa. In Figure \ref{fig-filter-progressive-noise}, we may see an image with different levels of noise, from 0\% to 45\% in steps of 5\%. It makes no sense to apply 50\% of noise because it would absolutely randomize the image.

\begin{figure}[!htb]
\centering\includegraphics[width=\textwidth]{./images02/filter/progressive-noise.png}
\caption{Progressive noise into letter ``A'', from 0\% to 45\% in steps of 5\%.
\label{fig-filter-progressive-noise}}
\end{figure}

The images have 30 x 30 pixels, totaling 900 pixels per image. Each image is mapped into a 1,000 bit bitstring in which the bits are set according to the color of each pixel of the image. White pixels are equal to bit 0, and black pixels to bit 1. The 100 remaining bits are all set to zero. This is a bijective mapping (or one-to-one) from images and bitstrings, i.e., there is one, and only one, bitstring for each image, and vice versa.

In the learning phase, noisy images are generated and they are written into SDM chunked with their labels. The chunk was calculated using the exclusive or (XOR) operator. So, the image bitstring was written to the address of its bitstrings XOR its label bitstring --- \pyth{write(addr=bs_image ^ bs_label, datum=bs_image)}.

Finally, in order to remove the noise of a new image, first we have to classify it (possibly using the already presented classification algorithm), and then we just have to read from the chunked address until it converges.

@@

Reinforcement learning has increasing prominence in the media after AlphaZero has won all games from both the best chess grandmasters in the world and the best chess engines. What is incredible about these victories is that AlphaZero has almost no knowledge about chess game and has learned all its movement playing against itself for 4 hours. Basically, it knowns only the valid movements and had to learn everything from scratch, which it did using a reinforcement learning algorithm.

Reinforcement learning is a machine learning algorithm which learns from the rewards of its actions. So, it receives the game state as input, then it decides which action will be taken, and finally it learns from the rewards of all the actions it has chosen. In theory, it learns after each reward feedback it receives, improving its decision over time and presenting intelligent behavior. A positive reward would indicate that the chosen action should be encouraged. While a negative reward would indicate the opposite. In some algorithms, there may be a neutral reward which would indicate that the chosen action was neither positive nor negative. How each type of reward should be handled depends on each algorithm.

We have done some experiments with an SDM as a memory for a TicTacToe player. Basically, it receives the current board state and returns which action should be played. In the end of the game, it receives the sequences of boards and the winner, and is supposed to learn from them.

Our algorithm to decide what should be player is very simples: it read the current board from SDM. If the reading converges to another board, it chooses the movement which would bring the current board to the one read from SDM. If the reading does not converge, it just play randomly.

After a game has finished, it is time to learn from its decisions. Thus, if SDM wins the game, it will write the whole sequence of boards to SDM. Let $b_0, b_1, b_2, \dots, b_n$ be the board sequence of the game. Then it will write $b_0 \rightarrow b_1 \rightarrow b_2 \rightarrow \cdots \rightarrow b_n$, with possibly different weights for each transition. If it loses, it will reverse the board (replace X by O and vice versa), and will act as if it had won. Hence, it will learn which sequences lead to victory. When a new board appears, it may have already seen that situation and will decide according to the sequences which goes towards victory. This is our positive reward learning.

It is also important to learn when a draw happens --- after all, it is better to tie than to lose, right? In this case, the sequence of boards is also written to SDM, but with no weight at all. So, if the board has appeared both in a tie sequence and in a winning sequence, it would be more likely to choose the winning one because it was written with greater weight. This is our neutral reward learning.

Finally, we also want to prevent losing games. So, when it loses a game, it will stimulate movements different from the chosen ones. Thus, for each transition $b_k \rightarrow b_{k+1}$ made by its action, it will write all possible transitions from $b_k$ but $b_{k+1}$.

Internally, every board is mapped into a random bitstring and passed to SDM. Thus, SDM knows nothing about the boards themselves. It knowns only about their transition and which ones would lead to either a victory or a draw. As every two boards are orthogonal, SDM does not known whether two boards are consecutives or not. The only link between two boards is the transition written in SDM.

After all, SDM knowns nothing about the boards themselves and yet it may learn how to play TicTacToe.

In order to properly run the discussed algorithms, it is necessary to have two SDMs: a 0-fold and a 1-fold SDM. In the 0-fold SDM, every bitstring is written to its own address. In the 1-fold SDM, every bitstring points somewhere else. So, the transitions are written in the 1-fold SDM, while the boards themselves are written to the 0-fold SDM. The boards are written only once in the 0-fold, no matter how many times they appear. The transitions may be written more than once in the 1-fold SDM, because it would reinforce that transition.

In more details, the next movement decision consists in one read from the 1-fold SDM, resulting in a bitstring. Then this bitstring is used in an interative reading from the 0-fold SDM, which will converge to the bitstring associated with the next board. If it does not converge to any board, than SDM will choose a random movement and learn from it.

The weight used when writing a winning sequence is calculated using ...

--- talk about player generations ---

\subsection{Training}

It is an unsupervised algorithm because SDM learns playing against an opponent, who may be another SDM player, a human, or a player whose movements are always aleatory.

Thus, in order to train a SDM player, we just have to keep it playing over and over.

\subsection{Results}
